---
title: "Hello R Markdown"
author: "Awesome Me"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

This is a paragraph in an [RMarkdown](https://rmarkdown.rstudio.com/) document.

#ggplot example


Below is a code chunk:

```{r}
library(tidyverse)

fit <- lm(dist ~ speed, data = cars)
b <- coef(fit)

ggplot(cars) +
  geom_smooth( aes( x = speed, 
                    y = dist ),
               method = lm)

```

The slope of the regression is `r b[2]`.


```{python}
x = 1
```

# Title

## Section X
This is my introduction.

## Quarterly Results {.tabset .tabset-fade .tabset-pills}
### By Product
(tab content)
### By Region
(tab content)



# Section 1 {.nextsteps, .emphasized}
Wake up
## Section 1.1
Drink water
## Section 1.2
Sleep again
# Section 2
Wake up

---
title: "Habits"
author: YOUR_NAME
date: January 31, 2023
output:
  html_document:
    toc: false
    toc_float: false
    number_sections: true
---
---
title: "Habits"
author: YOUR_NAME
date: January 31, 2023
output:
  html_document:
    toc: false
    toc_float: false
    number_sections: true
---

```{r, include=F}
library(fontawesome)
library(tidyverse)

```

```{r}
ggplot2::mpg
```

```{r setup, include = F}
library(tidyverse)
library(skimr)   # a better summary of data.frame
library(scales)  # scales for ggplot
library(ggthemes)  # additional ggplot themes
theme_set(theme_minimal()) # setting the minimal theme for ggplot
# setting default chunk options
knitr::opts_chunk$set(echo = T, eval = T,
                      message=F, warning = F) 
```

```{r}
library(gapminder)
gapminder
skim(gapminder)
```

```{r}
p <- ggplot(data = gapminder)
p <- ggplot(data = gapminder,
            mapping = aes(x = gdpPercap,
                          y = lifeExp))
p +geom_point()
```

```{r}
p + geom_point() + geom_smooth() 
p + geom_point() + geom_smooth(method = "lm") 
p + geom_point() +
    geom_smooth(method = "lm")
```

```{r}
p + geom_point() +
    geom_smooth(method = "gam")
```

```{r}
p2 <- ggplot(data = gapminder,
            mapping = aes(x = gdpPercap, y = lifeExp))
```

```{r}
p2 + geom_point(color = "purple") +
     geom_smooth(method = "lm")
```

```{r}
p <- ggplot(data = gapminder,
            mapping = aes(x = gdpPercap,
                          y = lifeExp))
p + geom_point(color = "purple") +
    geom_smooth(method = "loess") 
p + geom_point(alpha = 0.3) +
    geom_smooth(color = "orange", se = F, size = 8, method = "lm")
```

```{r}
p + geom_point(alpha = 0.3) +
    geom_smooth(method = "gam") +
    scale_x_log10(labels = scales::dollar) +
    labs(x = "GDP Per Capita", y = "Life Expectancy in Years",
         title = "Economic Growth and Life Expectancy",
         subtitle = "Data points are country-years",
         caption = "Source: Gapminder.")
```

```{r}
p <- ggplot(data = gapminder, 
            mapping = aes(x = gdpPercap, y = lifeExp))
p + geom_point(mapping = aes(color = continent)) +
    geom_smooth(method = "loess")  +
    scale_x_continuous(trans = scales::log_trans())  # natural log
```

```{r}
ggsave(filename = "my_figure.png")
```

```{r}
p_out <- p + geom_point() +
    geom_smooth(method = "loess") +
    scale_x_log10()
ggsave("my_figure.pdf", plot = p_out)
```

```{r}
ggsave("lifexp_vs_gdp_gradient.pdf",
       plot = p_out, height = 8, width = 10, units = "in")
```

```{r}
p <- ggplot(data = gapminder,
            mapping = aes( x = year,
                           y = gdpPercap ) )
p + geom_line()
```

```{r}
p <- ggplot(data = gapminder,
            mapping = aes( x = year,
                           y = gdpPercap ) )
p + geom_line( aes( group = country ) )
```

```{r}
p <- ggplot(data = gapminder,
            mapping = aes( x = year,
                           y = gdpPercap ) )
p + geom_line( aes( color = country ) )
```

```{r}
p + geom_line( aes( group = country ) ) + 
  facet_wrap(~ continent ~.)
```

```{r}
p + geom_line(color="gray70", aes(group = country)) +
    geom_smooth(size = 1.1, method = "loess", se = FALSE) +
    facet_grid(.~ continent) + #use grid as opposed to wrap
    scale_y_log10(labels=scales::dollar) + 
    theme(axis.text.x = element_text(angle = 45),
          axis.title.x = element_text(margin = margin(t = 25))) +
    labs(x = "Year", y = "GDP per capita",
         title = "GDP per capita on Five Continents")
```
```{r}
library(ggThemeAssist)
```

```{r}
ggplot(mpg)+
  geom_boxplot(aes(x= class, y = hwy))
```

```{r}
install.packages("socviz")
library(socviz)
?gss_sm
glimpse(gss_sm)
skimr::skim(gss_sm)
gss_sm <- gss_sm
```

```{r}
p <- ggplot(data = gss_sm,
            mapping = aes( x = age, y = childs ))

p + geom_point(alpha = 0.2) +
    geom_smooth(method = lm)
```

```{r}
p <- ggplot(data = gss_sm,
            mapping = aes( x = age, y = childs ))

p + geom_point(alpha = 0.2) +
    geom_smooth() +
    facet_grid(sex ~ race + degree)
```

```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = bigregion))
p + geom_bar()
```
```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = bigregion))
p + geom_bar(mapping = aes(y = ..prop.., group=1))
```
```{r}
table(gss_sm$religion)
```
```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = religion, color = religion))
p + geom_bar()
```
```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = religion, fill = religion))
p + geom_bar() + guides( fill = "none" )
```
```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = bigregion, fill = religion))
p + geom_bar(position = "fill")
```
```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = bigregion, fill = religion))
p + geom_bar(position = "dodge",
             mapping = aes(y = ..prop..))
```
```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = bigregion, fill = religion))
p + geom_bar(position = "dodge",
             mapping = aes(y = ..prop.., group = religion))
```
```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = religion))
p + geom_bar(position = "dodge",
             mapping = aes(y = ..prop.., group = bigregion)) +
    facet_wrap(~ bigregion, ncol = 1)
```
```{r}
?midwest
glimpse(midwest)
skim(midwest)
view(midwest)
```
```{r}
p <- ggplot(data = midwest,
            mapping = aes(x = area))
p + geom_histogram()
```
```{r}
p <- ggplot(data = midwest,
            mapping = aes(x = area))
p + geom_histogram(bins = 10)
```
```{r}
oh_wi <- c("OH", "WI")
p <- ggplot(data = filter(midwest, 
                          state %in% oh_wi),
            mapping = aes(x = percollege, fill = state) )
p + geom_histogram(alpha = 0.4, bins = 20)
```
```{r}
p <- ggplot(data = midwest,
            mapping = aes(x = area))
p + geom_density()
```
```{r}
p <- ggplot(data = midwest,
            mapping = aes(x = area, fill = state, color = state))
p + geom_density(alpha = 0.3)
```
```{r}
p <- ggplot(data = filter(midwest, state %in% oh_wi),
            mapping = aes(x = area, fill = state, color = state))
p + geom_density( alpha = 0.3, mapping =  aes(y = after_stat(scaled) )  )
```
```{r}
socviz::titanic
```
```{r}
p <- ggplot(data = titanic,
            mapping = aes(x = fate, y = percent, fill = sex))
p + geom_bar(position = "dodge", stat = "identity") +
  theme(legend.position = "top")
```
```{r}
oecd_sum
```


